### 2020-11-16 doc/manuscript/Dow_manuscript.Rmd
add Neil's references
updated name and affiliation
updated hypothesis table, knit in updated figures

Albert Kim^1^

@@

@@

```{r DOYtiming, out.width="100%", echo=FALSE, fig.align="center", fig.cap= DOYtiming_caption}
# Created in RScripts/additional_figures.R
knitr::include_graphics("tables_figures/DOYtiming.png")
```

@@

>>>>

Albert Y. Kim^1,2^

@@

2. Statistical & Data Sciences; Smith College; Northampton, MA 01063, USA

@@

```{r DOYtiming, out.width="100%", echo=FALSE, fig.align="center", fig.cap= DOYtiming_caption}
# Created in RScripts/additional_figures.R
knitr::include_graphics("tables_figures/DOYtiming_allyears.png")
```

@@

From Neil: @zhang_drought_2021, @zhang_extended_2020

effect of spring temperature on annual growth in New England: @alexander_potential_2019
